### 2020-03-08 short.body.tex
lunch time

In an epidemic, symptomatic cases are the predominant focus of treatment and usually represent the bulk of reported cases. 
However, infected individuals who are asymptomatic yet infectious can be a critical factor in the spread of some pathogens \citep{fraser2004factors}.
Asymptomatic individuals are hard to trace, unlikely to self-isolate, and are likely to retain normal social and travel patterns.
The COVID-19 outbreak has raised significant
questions regarding the role of asymptomatic cases~\citep{fauci_nejm2020}.
A key focus has been on estimating asymptomatic prevalence (see~\citep{mizumoto_2020}), e.g., what fraction of individuals have asymptomatic infections relative to those with symptomatic infections?

@@

Here, we focus on a third effect. 
If asymptomatic cases are important for transmission, they also have the potential to affect estimates of key parameters of disease spread such as the basic reproduction number ${\cal{R}}_0$ (i.e., the expected number of secondary cases generated by an average primary case in a fully susceptible population \citep{anderson1992infectious}). 
Here, we investigate the relationship between individual-level features of asymptomatic cases (e.g., the probability of initiating an asymptomatic case, asymptomatic case duration, and the transmission rates from asymptomatic individuals), which are represented by a generation-interval distribution, to dynamics at the population scale.
That is, rather than focusing on the prevalence
of asymptomatic cases, we are interested in understanding the
relevance of asymptomatic infections to secondary case production.

@@

@@

% The number of infected cases is expected to increase exponentially at rate $r$ at the outset of an outbreak.
We note that, in practice, counted cases may largely be of the symptomatic type.
Hence, we ask: is the expected ratio of incidence caused by asymptomatic cases vs.~symptomatic cases during the outbreak phase the same or different from $z/(1-z)$?
The ratio of secondary case production caused by asymptomatic vs.~symptomatic individuals over the course of an ongoing epidemic is
\begin{equation}
\frac{q}{1-q}=\frac{\mathcal R_a S(t) \int_0^\infty i_a(t-\tau) g_a(\tau) \mathrm{d}\tau}{\mathcal R_s S(t) \int_0^\infty i_s(t-\tau) g_s(\tau) \mathrm{d}\tau},
\end{equation}
where $q$ is the fraction of new secondary cases caused by asymptomatic individuals or `relevance' of asymptomatic cases.
Assuming that the incidence grows exponentially during the outbreak phase (i.e., $i(t) = i(0) \exp(r t)$) and substituting $i_a(t) = p i(t)$ and $i_s(t) = (1-p) i(t)$, we have
\begin{equation}
\frac{q}{1-q}=\left(\frac{z}{1-z}\right)\left[\frac{\int_0^\infty \exp(-r\tau) g_a(\tau) \mathrm{d}\tau}{\int_0^\infty \exp(-r\tau) g_s(\tau) \mathrm{d}\tau}\right].
\label{eq.qratio}
\end{equation}
The value of $q$ is an unknown feature of outbreaks at the population scale, distinct from $p$ the probability of becoming asymptomatic upon infection or $z$ the intrinsic proportion of asymptomatic transmission.

>>>>

In an epidemic, symptomatic cases are the predominant focus of treatment and usually represent the bulk of reported cases. 
However, infected individuals who are asymptomatic yet infectious can be a critical factor in the spread of some pathogens \citep{fraser2004factors}.
Asymptomatic individuals are hard to trace, unlikely to self-isolate, and are likely to retain normal social and travel patterns.

\jd{Delete this \P\ and roll the citations appropriately into the next one.}
The COVID-19 outbreak has raised significant
questions regarding the role of asymptomatic cases~\citep{fauci_nejm2020}.
A key focus has been on estimating asymptomatic prevalence (see~\citep{mizumoto_2020}), e.g., what fraction of individuals have asymptomatic infections relative to those with symptomatic infections?

@@

Here, we focus on a third effect. 
If asymptomatic cases are important for transmission, they also have the potential to affect estimates of key parameters of disease spread such as the basic reproduction number ${\cal{R}}_0$ (i.e., the expected number of secondary cases generated by an average primary case in a fully susceptible population \citep{anderson1992infectious}). 
Thus, we investigate the relationship between individual-level features of asymptomatic cases (e.g., the probability that an infection is asymptomatic, asymptomatic case duration, transmission by asymptomatic individuals) to dynamics at the population scale.

@@

\jd{Where should we citect champredon2015intrinsic if I delete the stuff below?}

@@

The intrinsic proporton of asymptomatic transmission $z$ is a useful benchmark, but does not necessarily reflect the realized proportion of asymptomatic transmission, unless both types of infection have the same generation-interval distribution.
The \emph{realized} proportion of asymptomatic transmission, $q$ at time $t$ is given by:
\begin{equation}
\frac{q}{1-q}=\frac{\mathcal R_a S(t) \int_0^\infty i_a(t-\tau) g_a(\tau) \mathrm{d}\tau}{\mathcal R_s S(t) \int_0^\infty i_s(t-\tau) g_s(\tau) \mathrm{d}\tau},
\end{equation}
During the period of exponential growth, we assume $S$ remains nearly constant, and $i(t)$ is proportional to $\exp(r t)$, and simplify: 
\begin{equation}
\frac{q}{1-q}=\left(\frac{z}{1-z}\right)\left[\frac{\int_0^\infty \exp(-r\tau) g_a(\tau) \mathrm{d}\tau}{\int_0^\infty \exp(-r\tau) g_s(\tau) \mathrm{d}\tau}\right].
\label{eq.qratio}
\end{equation}

\jd{Hi, Daniel!}
